### 2024-01-31 ms.qmd
Updates

#### Checking the models plots  
```{r, residuals}
# Chunk for calling all the models and making the residuals
## L. delicata
### Red
mod_dr <- readRDS(here("output/models/deli_red.rds"))
resid_dr <- residuals(mod_dr)
### Blue
mod_db <- readRDS(here("output/models/deli_blue.rds"))
resid_db <- residuals(mod_db)
## L. guichenoti
### Red
mod_gr <- readRDS(here("output/models/guich_red.rds"))
resid_gr <- residuals(mod_gr)
### Blue
mod_gb <- readRDS(here("output/models/guich_blue.rds"))
resid_gb <- residuals(mod_gb)
```

>>>>

#### Checking the models plots  
```{r, residuals}
# Chunk for calling all the models and making the residuals
## L. delicata
mod_deli <- readRDS(here("output/models/deli.rds"))
resid_deli <- residuals(mod_deli)
## L. guichenoti
mod_guich <- readRDS(here("output/models/guich.rds"))
resid_guich <- residuals(mod_guich)
```
